Letter to the Editor

### 2022-06-04 editorial-communication/cover-letter-submission.Rmd
Update cover-letter-submission.Rmd

Our manuscript is the most accessible and practical guide to using GitHub in ecology and evolution research to date.
We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research and ultimately supporting a better open and collaborative science.

>>>>

Our manuscript is the most accessible and practical guide to using GitHub in ecology and evolution research to date.
We build upon our own experiences (as an international collaboration from authors across many ecology and evolution subdisciplines) and on existing resources mainly targeted at other disciplines, to highlight how researchers can use the readily available GitHub suite to make their research practices reproducible, collaborative, and transparent.
Our manuscript is important for the *Nature Ecology & Evolution* readership because researchers in ecology and evolutionary biology can greatly benefit from our guide to migrate and incorporate GitHub workflows in their research practices ultimately towards an open and collaborative science.
